Opening the era of quasar host studies at high redshift with JWST

### 2022-11-03 projects/2022_CEERS_checkup/real_analysis/model_JWST_stage3_Masafusa/paper submit/submit/ding_jwst_v1.tex
For ceers and upcoming data

\software{\galight\citep{Ding2020,Ding2021a}, \lenstronomy~\citep{2018PDU....22..189B, 2021JOSS....6.3283B}, \texttt{gsf}~\citep{Morishita2019}, \texttt{psfr}\footnoteref{note1} (Birrer et al. in prep), \texttt{astropy}~\citep{2013A&A...558A..33A,2018AJ....156..123A}, \texttt{photutils}~\citep{larry_bradley_2020_4044744}}.

>>>>

\software{\galight~\citep{Ding2020,Ding2021a}, \lenstronomy~\citep{2018PDU....22..189B, 2021JOSS....6.3283B}, \texttt{gsf}~\citep{Morishita2019}, \texttt{psfr}\footnoteref{note1} (Birrer et al. in prep), \texttt{astropy}~\citep{2013A&A...558A..33A,2018AJ....156..123A}, \texttt{photutils}~\citep{larry_bradley_2020_4044744}}.
